---
title: "homework"
format: html
---

https://github.com/kai-s-suzuki/ENVS-193DS_homework-03

library(tidyverse)
library(here)
library(gt)
library(janitor)
library(readxl)
mydata <- read_csv("data/ENVS-193DS_caffeine_hw2.csv")

Problem 1. Personal Data

## a. 

I could calculate the mean caffeine consumed (mg) each day to compare how much caffeine is consumed between days with 0, 1, and 2 classes. Since I feel like I get more work done on days without classes and I have less commitments to prevent me from preparing or buying a caffeinated drink, it would make sense to compare means. 

## b.
```{r} 
# data wrangling
mydata_clean <- mydata |> # start mydata dataset
  filter(Classes %in% c("0", "1", "2")) |> # filter for 0, 1, or 2 classes
  mutate(Classes = as_factor(Classes)) |> # make sure classes (numerical) are being read in as a factor
  select(Classes, `Caffeine (mg)`, Ounces) |> # select columns of interest
  rename(caffeine_mg = `Caffeine (mg)`) # renaming caffeine column for ease
```

```{r}
# plot creation
ggplot(data = mydata_clean, # using the clean dataset
       aes(x = Classes, # setting x axis as classes
           y = caffeine_mg, # setting y axis as caffeine in mg
           color = Classes, # coloring by classes, so 0/1/2 have their own colors
           shape = Classes)) + # making sure 0/1/2 have their own shapes
  geom_boxplot() + # making boxplots
  geom_jitter(height = 0, # making sure the points don't move vertically
              width = 0.1) + # limiting how much the points move horizontally
  labs(y = "Caffeine (mg)") + # relabeling the y-axis
  theme_get() + # changing the theme
  scale_color_manual(values = c("0" = "darkgreen", # manually coloring 0, 1, and 2
                                "1" = "tan3",
                                "2" = "chocolate4")) +
   scale_shape_manual(values = c("0" = 17, "1" = 18, "2" = 19)) # making data points different shapes
```

